An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-03 paper/5.experiments.tex
edit caption table 1
fix ptail/bsnoc

\begin{table}[hbt!]
    \centering
    \caption{Composition test cases}
    \label{tab:test-cases}
    \begin{tabular*}{\textwidth}{|l @{\extracolsep{\fill}}|l|l|c|c|c|c|}
        \hline
        \multirow{2}{*}{No} & \multicolumn{1}{c|}{\multirow{2}{*}{Name}} & \multicolumn{1}{c|}{\multirow{2}{*}{Type}} & \multicolumn{2}{c|}{Input} & \multicolumn{2}{c|}{Output} \\ \cline{4-7} 
        & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{$s_0$} & \multicolumn{1}{c|}{$v_0$} & \multicolumn{1}{c|}{$s_r$} & \multicolumn{1}{c|}{$v_r$} \\ \hline
        1 & lcomp-phead-ldata & straight line & $\underbrace{[[\ldots[1]\ldots]]}_{\text{n+1 times}}$ & 100 & $\underbrace{[[\ldots[100]\ldots]]}_{\text{n+1 times}}$ & 1 \\ \hline
        2 & lcomp-ptail & straight line & [1,$\ldots$,n+1] & [1,$\ldots$,10] & $s_0 \ @ \ v_0$ & [\ ] \\ \hline
        3 & lcomp-ptail-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n+1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{10 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n+11 times}}$ & [\ ] \\ \hline
        4 & lcomp-bsnoc & straight line & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] \\ \hline
        5 & lcomp-bsnoc-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]]}_{\text{n-1 times}}$ \\ \hline
        6 & breverse & recursion & [1,$\ldots$,n] & [1,$\ldots$,n] & [n,$\ldots$,1] & [n,$\ldots$,1] \\ \hline
        7 & breverse-ldata & recursion & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ \\ \hline
    \end{tabular*}
\end{table}

@@

$\putbx{bsnoc}{s}{v}$ accepts a source $s$ and a view $v$, 
%as two same length lists, 
which are two lists of the same length,
and produces a new list by moving the last element of $v$ to its first position. $\getbx{ptail}{s}$ returns another list by moving the first element of the list $s$ to its end position. The composition of many \textit{ptail}, in the \textit{put} direction, creates a permutation of the view list if the source list has a same length as the view and, in the \textit{get} direction, produces a permutation of the source list.

>>>>

\begin{table}[hbt!]
    \centering
    \caption{Composition test cases (number of compositions = $n$)}
    \label{tab:test-cases}
    \begin{tabular*}{\textwidth}{|l @{\extracolsep{\fill}}|l|l|c|c|c|c|}
        \hline
        \multirow{2}{*}{No} & \multicolumn{1}{c|}{\multirow{2}{*}{Name}} & \multicolumn{1}{c|}{\multirow{2}{*}{Type}} & \multicolumn{2}{c|}{Input} & \multicolumn{2}{c|}{Output} \\ \cline{4-7} 
        & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{$s_0$} & \multicolumn{1}{c|}{$v_0$} & \multicolumn{1}{c|}{$s_r$} & \multicolumn{1}{c|}{$v_r$} \\ \hline
        1 & lcomp-phead-ldata & straight line & $\underbrace{[[\ldots[1]\ldots]]}_{\text{n+1 times}}$ & 100 & $\underbrace{[[\ldots[100]\ldots]]}_{\text{n+1 times}}$ & 1 \\ \hline
        2 & lcomp-ptail & straight line & [1,$\ldots$,n+1] & [1,$\ldots$,10] & $s_0 \ @ \ v_0$ & [\ ] \\ \hline
        3 & lcomp-ptail-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n+1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{10 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n+11 times}}$ & [\ ] \\ \hline
        4 & lcomp-bsnoc & straight line & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] & [1,$\ldots$,n-1] \\ \hline
        5 & lcomp-bsnoc-ldata & straight line & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n-1 times}}$ & $\underbrace{[L,\ldots,L]]}_{\text{n-1 times}}$ \\ \hline
        6 & breverse & recursion & [1,$\ldots$,n] & [1,$\ldots$,n] & [n,$\ldots$,1] & [n,$\ldots$,1] \\ \hline
        7 & breverse-ldata & recursion & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ & $\underbrace{[L,\ldots,L]}_{\text{n times}}$ \\ \hline
    \end{tabular*}
\end{table}

@@

$\putbx{bsnoc}{s}{v}$ accepts a source $s$ and a view $v$, 
%as two same length lists, 
which are two lists of the same length,
and produces a new list by moving the last element of $v$ to its first position. $\getbx{bsnoc}{s}$ returns another list by moving the first element of the list $s$ to its end position. The composition of many \textit{bsnoc}, in the \textit{put} direction, creates a permutation of the view list if the source list has a same length as the view and, in the \textit{get} direction, produces a permutation of the source list.
